\documentclass{article}
\usepackage{graphicx}
\title {\large {\textbf {Normal}} \\ \small {posts pour twitter}}

\begin{document}
\maketitle

\section {Self}
\begin{itemize}
\item What is your routined normal, what is your normal you cant live without
\item Whatever you have practiced the most (or had been repeated to you most) stays with you the longest. Say it and Do it more what you want to GetItDone.
\item Discipline is a habit like any other, except this time you are consciously building it. Same goes for fighting and giving your best for career and money. Most Indians are pragmatic as this is what they have seen all the time in their families.
\item life is not fair, get used to it, someone is very rich, someone begs for pennies all his life, someone never has a disease, someone's sick genetically, babies die in womb, - NOCES 
\item Zindagi main jo tum karna chah rahe ho, jaise apne lamho ko jeena chah rahe ho vaise jeene main aur vaise jeene ki koshish main lage rehne se badi nemat kuch bhi nahi hai, Zindagi Gulzar hai Zaroon's last scene. Insaan biwi bachchco ke saath khushi ke pal jeene se jyada kya umeed kar sakta hai, Forrest Gump - I ran, I felt like it. For me it is career or whatever, figure that out, kunas
\end{itemize}

\section {History}
\begin{itemize}
\item In 2023, if I had sat down doing boring ML, SQL and golang only for two fully days during late Aug 2023 to Feb 2024, I would have found motivation for a job and advanced in research as well rather than wasting more than 6 months from late August 2023 to Feb 2024. 

\end{itemize}

\section{People}
\begin{itemize}
\item Consider (and care for) those who first do for you. In general, do not give anyone more than he has already given you first.
\item Seedhe logo ka tej log kaise ch*iya bana dete hain aur use ban kar achcha lagta hai (chaya's brother Siddhartha fooled by Kartik over leftovers of March 12th)

\end{itemize}

 \end{document}
